Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-05 RR_manuscript/Draft_RR.Rmd
fixes #270

In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.

>>>>

In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials at <https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf>.

### 2022-11-05 RR_manuscript/Draft_RR.tex
fixes #270

In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.

>>>>

In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials at \url{https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf}.
